### 2023-08-22 paper/paper-papaja.Rmd
fixed typos

keywords          : "Illusory truth; Metacognition; Cognitive Psychology; Misinformation"
wordcount         : "4929"

@@

```{r fig1, fig.env="figure", fig.pos = "h", fig.align = "center", fig.cap="Average truth ratings for Implication statements in Experiment 1, broken down by exposure (exposed vs. unexposed), instructions (fact vs quiz conditions), implication type (true-implied-false vs false-implied-true). For visualization purposes, means were calcaulated by translating ordinal responses onto a scale from -2.5 to 2.5. Error bars indicate standard errors. "}
fig1 <- df %>% 
  filter(phase=="test") %>% 
  filter(item_type == "B") %>% 
  group_by(exposed, exposure_cond, B_implied_true) %>% 
  summarize(
    M = mean(resp_num),
    se = sd(resp_num)/sqrt(n()),
    ll = M - se,
    ul = M + se
  ) %>% 
  mutate(
    exposure_cond = if_else(exposure_cond=="fact", "Fact condition", "Quiz condition"),
    exposed = if_else(exposed==1, "Exposed", "Unexposed"),
    B_implied_true = as.character(B_implied_true)
    ) %>% 
  ggplot(
    aes(x=B_implied_true, color=factor(exposed), shape=factor(exposed), y = M, ymin = ll, ymax=ul)
  ) +
  geom_pointrange(position=position_dodge(width=.5)) +
  # coord_flip() +
  scale_color_manual(values = c("#da1e28", "#0f62fe")) +
  labs(y = "Truth rating", x = "Implication type", color="Exposure", shape="Exposure") +
  facet_wrap(~exposure_cond) +
  theme_bw(base_size=9.5) +
  theme(panel.grid=element_blank(), legend.position="bottom") +
  theme(axis.text.x = element_text(angle = 10, vjust = 0.5, hjust=.5))

@@

```{r fig2, fig.env="figure", fig.pos = "t", fig.align = "center", fig.cap="Average truth ratings for Implication statements in Experiment 2, broken down by exposure (exposed vs. unexposed) and implication type (true-implied-false vs false-implied-true). For visualization purposes, means were calcaulated by translating ordinal responses onto a scale from -2.5 to 2.5. Error bars indicate standard errors."}

@@

```{r fig3, fig.env="figure*", fig.pos = "!hbt", fig.align = "center", fig.width=6.5, fig.height=3, fig.cap="Average truth ratings for individual premise and implication statements in Experiment 2, broken down by exposure (exposed vs. unexposed) and implication type (true-implied-false vs false-implied-true). For visualization purposes, means were calcaulated by translating ordinal responses onto a scale from -2.5 to 2.5. Error bars indicate standard errors.", num.cols.cap=2}

@@

All item pairs were identical to Experiment 2. However, several changes were made to the study's procedures limit the potential that the illusory implication effect could be produced by idiosyncratic features of the experimental task.

@@

To improve our ability to measure the implication effect, in Experiment 3 participants were exposed to 12 of the premise statements at exposure rather than eight. As a consequence, we did not examine illusory truth effects. The 24 premise statements were randomly sorted in to 12 comparison questions, and each participant saw 6 of these pairs at exposure, along with five control pairs.

Following the test phase, two new questions assessed the potential influence of task demands. Participants were asked if they ever suspected the study had an undisclosed purpose (yes/no), and then regardless of their answer asked to explained their suspicions in an open-ended response. Responses were coded to identify participants who guessed that the true purpose concerned how their responses to the test phase would be affected by the exposure phase or by seeing misinformation. These participants were excluded from certain analyses following our pre-registered analysis plan.

@@

```{r fig-exp3, fig.align='center', fig.cap="Average truth ratings for Implication statements in Experiment 3, broken down by exposure (exposed vs. unexposed) and implication type (true-implied-false vs false-implied-true). For visualization purposes, means were calcaulated by translating ordinal responses onto a scale from -2.5 to 2.5. Error bars indicate standard errors."}

df3 %>% 
  filter(phase=="test") %>% 
  filter(item_type == "B") %>% 
  mutate(
    exposed = if_else(exposed, "Exposed", "Unexposed")
  ) %>% 
  group_by(exposed, B_implied_true) %>% 
  summarize(
    M = mean(resp_num),
    se = sd(resp_num)/sqrt(n()),
    ll = M - se,
    ul = M + se
  ) %>% 
  ggplot(
    aes(x=B_implied_true, color=factor(exposed), shape=factor(exposed), y = M, ymin = ll, ymax=ul)
  ) +
  geom_pointrange(position=position_dodge(width=.5))  +
  scale_color_manual(values = c("#da1e28", "#0f62fe")) +
  theme_bw(base_size=10) +
  theme(legend.position="bottom", panel.grid=element_blank()) +
  # coord_flip() +
  labs(y = "Truth rating", x = "Implication type", color="Exposure", shape="Exposure")
```

@@

Next, to explore the possibility that these results might be influenced by task demands, we also carried out a parallel analysis excluding participants whose responses may have been impacted by their suspicions as to the true purpose of the study [@coles.frank2023]. We excluded both participants who explicitly stated they were suspicious when asked directly, and those who forced to guess in an open-ended response, guessed that the true purpose had to do with the first phase somehow affecting their responses in the second. Removing these participants did not substantially change the estimate of the implication effect, $\beta =$ `r report_reg_coef(fit_imp_maximal3, "implication")`.

>>>>

keywords          : "Illusory truth; Metacognition; Cognitive Psychology; Misinformation"
wordcount         : "4930"

@@

```{r fig1, fig.env="figure", fig.pos = "h", fig.align = "center", fig.cap="Average truth ratings for Implication statements in Experiment 1, broken down by exposure (exposed vs. unexposed), instructions (fact vs quiz conditions), implication type (false-implied-true vs true-implied-false). For visualization purposes, means were calculated by translating ordinal responses onto a scale from -2.5 to 2.5. Error bars indicate standard errors. "}
fig1 <- df %>% 
  filter(phase=="test") %>% 
  filter(item_type == "B") %>% 
  group_by(exposed, exposure_cond, B_implied_true) %>% 
  summarize(
    M = mean(resp_num),
    se = sd(resp_num)/sqrt(n()),
    ll = M - se,
    ul = M + se
  ) %>% 
  mutate(
    exposure_cond = if_else(exposure_cond=="fact", "Fact condition", "Quiz condition"),
    exposed = if_else(exposed==1, "Exposed", "Unexposed"),
    B_implied_true = as.character(B_implied_true)
    ) %>% 
  ggplot(
    aes(x=B_implied_true, color=factor(exposed), shape=factor(exposed), y = M, ymin = ll, ymax=ul)
  ) +
  geom_pointrange(position=position_dodge(width=.5)) +
  # coord_flip() +
  scale_color_manual(values = c("#da1e28", "#0f62fe")) +
  labs(y = "Truth rating", x = "Implication type", color="Exposure", shape="Exposure") +
  facet_wrap(~exposure_cond) +
  theme_bw(base_size=9.5) +
  theme(panel.grid=element_blank(), legend.position="bottom") +
  theme(axis.text.x = element_text(angle = 10, vjust = 0.5, hjust=.5))

@@

```{r fig2, fig.env="figure", fig.pos = "t", fig.align = "center", fig.cap="Average truth ratings for Implication statements in Experiment 2, broken down by exposure (exposed vs. unexposed) and implication type (false-implied-true vs true-implied-false). For visualization purposes, means were calculated by translating ordinal responses onto a scale from -2.5 to 2.5. Error bars indicate standard errors."}

@@

```{r fig3, fig.env="figure*", fig.pos = "!hbt", fig.align = "center", fig.width=6.5, fig.height=3, fig.cap="Average truth ratings for individual premise and implication statements in Experiment 2, broken down by exposure (exposed vs. unexposed) and implication type (false-implied-true vs true-implied-false). For visualization purposes, means were calculated by translating ordinal responses onto a scale from -2.5 to 2.5. Error bars indicate standard errors.", num.cols.cap=2}

@@

All item pairs were identical to Experiment 2. However, several changes were made to the study's procedures to limit the potential that the illusory implication effect could be produced by idiosyncratic features of the experimental task.

@@

To improve our ability to measure the implication effect, in Experiment 3 participants were exposed to 12 of the premise statements at exposure rather than eight. As a consequence, we did not examine illusory truth effects. The 24 premise statements were randomly sorted into 12 comparison questions, and each participant saw 6 of these pairs at exposure, along with five control pairs.

Following the test phase, two new questions assessed the potential influence of task demands. Participants were asked if they ever suspected the study had an undisclosed purpose (yes/no), and then regardless of their answer asked to explain their suspicions in an open-ended response. Responses were coded to identify participants who guessed that the true purpose concerned how their responses to the test phase would be affected by the exposure phase or by seeing misinformation. These participants were excluded from certain analyses following our pre-registered analysis plan.

@@

```{r fig-exp3, fig.align='center', fig.cap="Average truth ratings for Implication statements in Experiment 3, broken down by exposure (exposed vs. unexposed) and implication type (false-implied-true vs true-implied-false). For visualization purposes, means were calculated by translating ordinal responses onto a scale from -2.5 to 2.5. Error bars indicate standard errors."}

df3 %>% 
  filter(phase=="test") %>% 
  filter(item_type == "B") %>% 
  mutate(
    exposed = if_else(exposed, "Exposed", "Unexposed")
  ) %>% 
  group_by(exposed, B_implied_true) %>% 
  summarize(
    M = mean(resp_num),
    se = sd(resp_num)/sqrt(n()),
    ll = M - se,
    ul = M + se
  ) %>% 
  mutate(B_implied_true = ordered(B_implied_true, levels = c("F implied T", "T implied F"))) %>% 
  ggplot(
    aes(x=B_implied_true, color=factor(exposed), shape=factor(exposed), y = M, ymin = ll, ymax=ul)
  ) +
  geom_pointrange(position=position_dodge(width=.5))  +
  scale_color_manual(values = c("#da1e28", "#0f62fe")) +
  theme_bw(base_size=10) +
  theme(legend.position="bottom", panel.grid=element_blank()) +
  # coord_flip() +
  labs(y = "Truth rating", x = "Implication type", color="Exposure", shape="Exposure")
```

@@

Next, to explore the possibility that these results might be influenced by task demands, we also carried out a parallel analysis excluding participants whose responses may have been impacted by their suspicions as to the true purpose of the study [@coles.frank2023]. We excluded both participants who explicitly stated they were suspicious when asked directly, and those who, when forced to guess in an open-ended response, guessed that the true purpose had to do with the first phase somehow affecting their responses in the second. Removing these participants did not substantially change the estimate of the implication effect, $\beta =$ `r report_reg_coef(fit_imp_maximal3, "implication")`.
